### 2018-02-01 includes/introduction.tex
Reverting some changes addressed in review. Made tables look scientific. Made sure tables were no longer than line width. Added footnotes rather than column for Ifaz transformations.
Typo.

Fuzzing has been used to test all kinds of software
including SAT solvers~\cite{fuzzsat}. Inspired by these fuzzers,
we introduce \fuzzer{} and describe its value
as an exploratory testing tool. We demonstrate its efficacy
by presenting limitations it helped discover in
leading string solvers. To the best of our knowledge, \fuzzer{} is the
only tool aimed at automatic generation of string constraints. \fuzzer{} can
be used to mutate or transform existing benchmarks, as well as
randomly generate structured instances. These instances can be scaled with
respect to a variety of parameters, e.g., length of string constants,
depth of concatenations (concats) and regular expressions, number of variables,
number of length constraints, and many more.

@@

    \item \textbf{Experimental Results and Analysis}:
        We compare the performance of \theSolvers{} on the
        the \fuzzer{} suites \theSuites{} in Sect.~\ref{sec:data}. We
        highlight these suites because they make some solvers perform poorly,
        but not others. We analyze our
        experimental results, and pinpoint algorithmic limitations
        in \us{} that cause poor performance.
\end{enumerate}

>>>>

Fuzzing has been used to test all kinds of software
including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
we introduce \fuzzer{} and describe its value
as an exploratory testing tool. We demonstrate its efficacy
by presenting limitations it helped discover in
leading string solvers. To the best of our knowledge, \fuzzer{} is the
only tool aimed at automatic generation of string constraints. \fuzzer{} can
be used to mutate or transform existing benchmarks, as well as
randomly generate structured instances. These instances can be scaled with
respect to a variety of parameters, e.g., length of string constants,
depth of concatenations (concats) and regular expressions, number of variables,
number of length constraints, and many more.

@@

    \item \textbf{Experimental Results and Analysis}:
        We compare the performance of \theSolvers{} on the
        \fuzzer{} suites \theSuites{} in Sect.~\ref{sec:data}. We
        highlight these suites because they make some solvers perform poorly,
        but not others. We analyze our
        experimental results, and pinpoint algorithmic limitations
        in \us{} that cause poor performance.
\end{enumerate}
